A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-31 12_conclusions_future_work.tex
Tim: finetune conclusion etc

We presented the inward distributed beading scheme.
It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in case of wide contours, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.

>>>>

We presented the inward distributed beading scheme.
It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
which in turn can be helpful to efficiently simulate an FDM manufactured part.
Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.

### 2019-08-31 1_intro.tex
Tim: finetune conclusion etc

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
Therefore, a narrower range of widths is desirable.

>>>>

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
Therefore, a narrower range of widths is desirable.
